full title

### 2020-11-21 paper/pldi21/eval.tex
Temporal dump

\begin{figure}[t]
  \centering
  \includegraphics[width=\linewidth]{img/abs-analysis-ratio}
  \vspace*{-1.5em}
  \caption{Analysis time ratio for \inred{219} \textit{abstracted} tests}
  \label{fig:abs-analysis-ratio}
  \vspace*{-1.5em}
\end{figure}

Unlike for the original tests, analysis of \inred{82}
abstracted tests that are analyzable by both analyzers invoked
\inred{xx} dynamic shortcuts.  Because taking a dynamic shortcut
requires converting between abstract states and sealed symbolic values
and exchanging them between the static analyzer and the dynamic analyzer,
using dynamic shortcuts multiple times may incur more performance
overhead than performance benefits by using sealed symbolic execution.
One may conjecture that the communication cost between the static
analyzer and the dynamic analyzer may be proportional to the number of
dynamic shortcuts.

To experimentally evaluate the conjecture, we investigated the relationship between
the communication cost between analyzers and the number of dynamic shortcuts.
For \inred{xx} original tests, the communication cost was only
\inred{x.xx}\% of the total analysis time.  However, for \inred{xx}
abstracted tests, the communication cost was \inred{xx.xx}\% of the
total analysis time.  Figure~\ref{fig:abs-analysis-ratio} presents the
analysis time ratio for \inred{82} abstracted tests.
The $x$-axis represents the time ratio normalized by the total analysis time with dynamic shortcuts
and the $y$-axis denotes the number of dynamic shortcuts and the number of corresponding tests.
For all \inred{82} tests, the communication cost (DS-Comm.) is larger than
both the static analysis time (DS-Static) and the dynamic analysis
time (DS-Dynamic).  When dynamic shortcuts are performed less than 10 times,
the communication cost is modest compared with the baseline static
analysis time (no-DS).  However, the more dynamic shortcuts are performed,
the less the performance benefits by using sealed symbolic execution.
Specifically, when dynamic shortcuts are performed more than
\inred{30} times, DS-Comm. is even larger than no-DS.
Based on this evaluation result, we believe that we can leverage
dynamic shortcuts by optimizing the communication between static and dynamic analyzers.

\begin{figure}[t]
  \centering
  \begin{subfigure}[t]{0.48\textwidth}
    \includegraphics[width=\linewidth]{img/conc-precision}
    \vspace*{-1.5em}
    \caption{Reachable branches for \inred{xx} \textit{original} tests}
    \label{fig:precision-fail}
  \end{subfigure}
  \begin{subfigure}[t]{0.48\textwidth}
    \includegraphics[width=\linewidth]{img/abs-precision}
    \vspace*{-1.5em}
    \caption{Reachable branches for \inred{82} \textit{abstracted} tests}
    \label{fig:precision-branch}
  \end{subfigure}
  \vspace*{-1em}
  \caption{Branch coverage of analysis without (no-DS) and with (DS) dynamic shortcuts}
  \label{fig:precision}
  \vspace*{-1.5em}
\end{figure}

\begin{table*}[t]
  \centering
  \caption{The number of \textit{abstracted} tests using dynamic shortcut
  instead of manual modeling for each JavaScript built-in library}
  \label{table:func-replace}
  \vspace*{-1em}
  \scriptsize
  \[
    \begin{array}{c|l|@{~}r@{~}c@{~}r@{~}r@{~}?c|l|@{~}r@{~}c@{~}r@{~}r@{~}?c|l|@{~}r@{~}c@{~}r@{~}r@{~}}

@@

      \mysucc{2}{Boolean}   {Boolean}         {214}{214}{100} & \mydata{1}{}            {new Object}        {214}{214}{100} & \mymult{2}{Number}      {valueOf}       {214}{214}{100} \mylineff
      \mydata{1}{}          {new Boolean}     {214}{214}{100} & \mydata{1}{}            {getPrototypeOf}    {214}{214}{100} & \myname{1}{.prototype}                                  \mylinetft
      \mydata{1}{Array}     {isArray}         {214}{214}{100} & \mydata{1}{}            {create}            {214}{214}{100} & \mymult{2}{RegExp}      {toString}      {214}{214}{100} \mylinetf
      \mydata{1}{}          {toString}        { 92}{139}{ 66} & \mydata{1}{Object}      {preventExtensions} {214}{214}{100} & \myname{1}{.prototype}                                  \mylinefft
      \mydata{1}{}          {toLocaleString}  {193}{214}{ 90} & \mydata{1}{}            {isFrozen}          {214}{214}{100} & \mydata{2}{String}      {String}        {214}{214}{100} \mylinefff
      \mydata{1}{}          {concat}          {214}{214}{100} & \mydata{1}{}            {isExtensible}      {214}{214}{100} & \mydata{1}{}            {fromCharCode}  {214}{214}{100} \mylinefft
      \mydata{1}{}          {join}            {214}{214}{100} & \mydata{1}{}            {keys}              {214}{214}{100} & \mydata{1}{}            {charAt}        {214}{214}{100} \mylineftf
      \mysucc{1}{Array}     {pop}             {214}{214}{100} & \mydata{1}{Object}      {valueOf}           {214}{214}{100} & \mydata{1}{}            {charCodeAt}    {214}{214}{100} \mylinefff
      \mydata{1}{.prototype}{push}            {214}{214}{100} & \mydata{1}{.prototype}  {isPrototypeOf}     {214}{214}{100} & \mydata{1}{}            {indexOf}       {214}{214}{100} \mylineftf
      \mydata{1}{}          {slice}           {214}{214}{100} & \mydata{1}{}            {acos}              {214}{214}{100} & \mysucc{1}{}            {match}         {214}{214}{100} \mylinefff
      \mydata{1}{}          {splice}          {214}{214}{100} & \mysucc{1}{}            {atan2}             {214}{214}{100} & \mydata{1}{String}      {replace}       {214}{214}{100} \mylinefff
      \mydata{1}{}          {map}             {214}{214}{100} & \mydata{1}{}            {cos}               {214}{214}{100} & \mydata{1}{.prototype}  {splice}        {214}{214}{100} \mylinefff
      \mydata{1}{}          {reduce}          {214}{214}{100} & \mydata{1}{Math}        {exp}               {214}{214}{100} & \mydata{1}{}            {split}         {214}{214}{100} \mylinetff
      \mysucc{1}{global}    {eval}            {214}{214}{100} & \mydata{1}{}            {floor}             {214}{214}{100} & \mysucc{1}{}            {substring}     {214}{214}{100} \mylinetff
      \mydata{1}{}          {new Date}        {214}{214}{100} & \mydata{1}{}            {max}               {214}{214}{100} & \mydata{1}{}            {toLowerCase}   {214}{214}{100} \mylinefff
      \mydata{1}{Date}      {parse}           {214}{214}{100} & \mydata{1}{}            {min}               {214}{214}{100} & \mydata{1}{}            {toUpperCase}   {214}{214}{100} \mylinef
      \mydata{1}{}          {now}             {214}{214}{100}
    \end{array}
  \]
  \vspace*{-1em}
\end{table*}

@@

Figure~\ref{fig:precision} depicts the comparison of the analysis
precision between no-DS and DS.  The $x$-axis and the $y$-axis denote
the number of branches covered by no-DS and DS, respectively;
each $\times$ mark denotes each test.  The top and bottom dotted lines
denote the worst and the best precision improvement, respectively, and
the middle solid line denotes the average improvement.
For \inred{xx} original tests that are analyzable by both analyzers,
Figure~\ref{fig:precision}(a) shows that dynamic shortcuts
successfully reduced the number of covered branches at least
\inred{1.00}\textsc{x}, at most \inred{0.54}\textsc{x}, and \inred{0.92}x on average.
For \inred{xx} abstracted tests that are analyzable by both analyzers,
Figure~\ref{fig:precision}(b) shows that dynamic shortcuts
also successfully cut down the number of covered branches at least
\inred{0.81}\textsc{x}, at most \inred{0.51}\textsc{x}, and \inred{0.68}\textsc{x} on average.

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=\linewidth]{img/abs-analysis-ratio}
  \vspace*{-1.5em}
  \caption{Analysis time ratio for 143 \textit{abstracted} tests}
  \label{fig:abs-analysis-ratio}
  \vspace*{-1.5em}
\end{figure}

\begin{table*}[t]
  \centering
  \caption{The number of \textit{abstracted} tests using dynamic shortcut
  instead of manual modeling for each JavaScript built-in library}
  \label{table:func-replace}
  \vspace*{-1em}
  \scriptsize
  \[
    \begin{array}{c|l|c|c?c|l|c|c?c|l|c|c}

@@

      \mydata{1}{}          {Array    }  {214 / 214}{214 / 214} & \mydata{1}{}             {String     }  {214 / 214}{214 / 214} & \mydata{1}{}       {Object        }  {214 / 214}{214 / 214} \mylinefff
      \mydata{1}{}          {new Array}  {214 / 214}{214 / 214} & \mydata{1}{}             {toString   }  {214 / 214}{214 / 214} & \mydata{1}{}       {new Object    }  {214 / 214}{214 / 214} \mylinefff
      \mydata{1}{}          {isArray  }  {214 / 214}{214 / 214} & \mydata{1}{}             {valueOf    }  {214 / 214}{214 / 214} & \mydata{1}{}       {getPrototypeOf}  {214 / 214}{214 / 214} \mylinetff
      \mydata{1}{}          {concat   }  { 92 /  92}{139 /  92} & \mysucc{1}{}             {charAt     }  {214 /  92}{214 /  92} & \mydata{1}{}       {create        }  {214 /  92}{214 /  92} \mylinetff
      \mydata{1}{}          {join     }  {193 / 193}{214 / 193} & \mydata{1}{}             {charCodeAt }  {214 / 193}{214 / 193} & \mydata{1}{Object} {defineProperty}  {214 / 193}{214 / 193} \mylinefff
      \mydata{1}{}          {pop      }  {214 / 214}{214 / 214} & \mydata{1}{}             {indexOf    }  {214 / 214}{214 / 214} & \mydata{1}{}       {freeze        }  {214 / 214}{214 / 214} \mylinefft
      \mydata{2}{Array}     {push     }  {214 / 214}{214 / 214} & \mydata{1}{String}       {match      }  {214 / 214}{214 / 214} & \mydata{1}{}       {keys          }  {214 / 214}{214 / 214} \mylineftf
      \mysucc{1}{}          {reverse  }  {214 / 214}{214 / 214} & \mydata{1}{}             {replace    }  {214 / 214}{214 / 214} & \mydata{1}{}       {toString      }  {214 / 214}{214 / 214} \mylinefff
      \mydata{1}{}          {shift    }  {214 / 214}{214 / 214} & \mydata{1}{}             {slice      }  {214 / 214}{214 / 214} & \mydata{1}{}       {hasOwnProperty}  {214 / 214}{214 / 214} \mylineftf
      \mydata{1}{}          {slice    }  {214 / 214}{214 / 214} & \mydata{1}{}             {split      }  {214 / 214}{214 / 214} & \mysucc{1}{}       {parseInt}        {214 / 214}{214 / 214} \mylinefff
      \mydata{1}{}          {sort     }  {214 / 214}{214 / 214} & \mydata{1}{}             {substring  }  {214 / 214}{214 / 214} & \mydata{1}{Global} {isNaN   }        {214 / 214}{214 / 214} \mylinefff
      \mydata{1}{}          {splice   }  {214 / 214}{214 / 214} & \mydata{1}{}             {toLowerCase}  {214 / 214}{214 / 214} & \mydata{1}{}       {isFinite}        {214 / 214}{214 / 214} \mylinefff
      \mydata{1}{}          {unshift  }  {214 / 214}{214 / 214} & \mydata{1}{}             {toUpperCase}  {214 / 214}{214 / 214} & \mydata{1}{}       {RegExp    }      {214 / 214}{214 / 214} \mylinetff
      \mysucc{1}{}          {indexOf  }  {214 / 214}{214 / 214} & \mydata{2}{Boolean}      {Boolean}      {214 / 214}{214 / 214} & \mysucc{2}{RegExp} {new RegExp}      {214 / 214}{214 / 214} \mylinetff
      \mydata{1}{}          {every    }  {214 / 214}{214 / 214} & \mydata{1}{}             {valueOf}      {214 / 214}{214 / 214} & \mydata{1}{}       {exec      }      {214 / 214}{214 / 214} \mylinefff
      \mydata{1}{}          {ceil }      {214 / 214}{214 / 214} & \mydata{2}{Number}       {Number }      {214 / 214}{214 / 214} & \mydata{1}{}       {test      }      {214 / 214}{214 / 214} \mylinefff
      \mydata{1}{}          {floor}      {214 / 214}{214 / 214} & \mydata{1}{}             {valueOf}      {214 / 214}{214 / 214} & \mydata{1}{}       {Error         }  {214 / 214}{214 / 214} \mylinefff
      \mydata{1}{Math}      {max  }      {214 / 214}{214 / 214} & \mydata{1}{}             {toString}     {214 / 214}{214 / 214} & \mydata{2}{Error}  {new Error     }  {214 / 214}{214 / 214} \mylinefff
      \mydata{1}{}          {min  }      {214 / 214}{214 / 214} & \mydata{1}{Function}     {apply   }     {214 / 214}{214 / 214} & \mydata{1}{}       {new RangeError}  {214 / 214}{214 / 214} \mylinefff
      \mydata{1}{}          {pow  }      {214 / 214}{214 / 214} & \mydata{1}{}             {call    }     {214 / 214}{214 / 214} & \mydata{1}{}       {new TypeError }  {214 / 214}{214 / 214}
    \end{array}
  \]
  \vspace*{-1em}
\end{table*}

Unlike for the original tests, analysis of 143
abstracted tests that are analyzable by both analyzers invoked
16.05 dynamic shortcuts.  Because taking a dynamic shortcut
requires converting between abstract states and sealed symbolic values
and exchanging them between the static analyzer and the dynamic analyzer,
using dynamic shortcuts multiple times may incur more performance
overhead than performance benefits by using sealed symbolic execution.
One may conjecture that the communication cost between the static
analyzer and the dynamic analyzer may be proportional to the number of
dynamic shortcuts.

\todo
To experimentally evaluate the conjecture, we investigated the relationship between
the communication cost between analyzers and the number of dynamic shortcuts.
For 198 original tests, the communication cost was only
\inred{x.xx}\% of the total analysis time.  However, for 143
abstracted tests, the communication cost was \inred{xx.xx}\% of the
total analysis time.  Figure~\ref{fig:abs-analysis-ratio} presents the
analysis time ratio for 143 abstracted tests.
The $x$-axis represents the time ratio normalized by the total analysis time with dynamic shortcuts
and the $y$-axis denotes the number of dynamic shortcuts and the number of corresponding tests.
For all 143 tests, the communication cost (DS-Comm.) is larger than
both the static analysis time (DS-Static) and the dynamic analysis
time (DS-Dynamic).  When dynamic shortcuts are performed less than 10 times,
the communication cost is modest compared with the baseline static
analysis time (no-DS).  However, the more dynamic shortcuts are performed,
the less the performance benefits by using sealed symbolic execution.
Specifically, when dynamic shortcuts are performed more than
\inred{30} times, DS-Comm. is even larger than no-DS.
Based on this evaluation result, we believe that we can leverage
dynamic shortcuts by optimizing the communication between static and dynamic analyzers.

\begin{figure}[t]
  \centering
  \begin{subfigure}[t]{0.48\textwidth}
    \includegraphics[width=\linewidth]{img/conc-precision}
    \vspace*{-1.5em}
    \caption{Reachable branches for 198 \textit{original} tests}
    \label{fig:precision-fail}
  \end{subfigure}
  \begin{subfigure}[t]{0.48\textwidth}
    \includegraphics[width=\linewidth]{img/abs-precision}
    \vspace*{-1.5em}
    \caption{Reachable branches for 143 \textit{abstracted} tests}
    \label{fig:precision-branch}
  \end{subfigure}
  \vspace*{-1em}
  \caption{Branch coverage of analysis without (no-DS) and with (DS) dynamic shortcuts}
  \label{fig:precision}
  \vspace*{-1.5em}
\end{figure}

@@

Figure~\ref{fig:precision} depicts the comparison of the analysis
precision between no-DS and DS.  The $x$-axis and the $y$-axis denote
the number of branches covered by no-DS and DS, respectively;
each $\times$ mark denotes each test.  The top and bottom dotted lines
denote the worst and the best precision improvement, respectively, and
the middle solid line denotes the average improvement.
For 198 original tests that are analyzable by both analyzers,
Figure~\ref{fig:precision}(a) shows that dynamic shortcuts
reduced the number of covered branches at most 13.13\%. However, it reduced
the number of branches 0.46\% on average because the most of original tests
use concrete values without any non-determinism. Unlike original tets, for 143
abstracted tests that are analyzable by both analyzers,
Figure~\ref{fig:precision}(b) shows that dynamic shortcuts successfully cut down
the number of covered branches at most 13.65\% and 1.89\% on average.  In other
words, the dynamic shortcuts prevent to analyze 1.44 and 5.97 spurious branches
for original and abstracted tests on average.
